Initial Analysis

### 2019-08-21 Initial_Analysis.Rmd
Included time that took to run model in the Beast
Created a function to do the analysis per dataset

#### Library ####
packages <- c(
  "readxl", # Read dataframe
  "data.table", # Read dataframe (Fast!)
  "dplyr", # Data manipulation
  "tidyr", # Data manipulation
  "ggplot2", #Nice grpahs and spatial analysis
  "wesanderson",
  # "cowplot",
  # "rgdal",
  # "RColorBrewer",
  # "knitr",
  # "kableExtra",
  # "ggrepel",
  # "gridExtra",
  # "ggmap",
  # "rgeos",
  # "stringr",
  # "stringer",
  "spdep", # for poly2nb
  "sf", #Spatial analysis 
  "sp", #Spatial analysis 
  "purrr",#Spatial analysis
  "rgdal", #Spatial analysis
  "tools", #Spatial analysis 
  # "png", # For reading plots in chunk codes
  # "grid" # For reading plots in chunk codes
  "parallel" # for parallelization
)

@@

@@

  #____________ ESTIMATING MODEL INDEX (TRESHOLD 1)_________ #
  Trans_Spp <- SppDist %>%
    filter(INDEX %in% Neighbors$INDEX,# Filter data only located within EEZs
           Model != "SAU_C") %>% # Only using observational and modelled data
    mutate(Value = ifelse(Value > 0, 1,0)) %>%  
    filter(Value > 0) %>%  # Remove latter, just keeps places with 1
    # Commented out to produce a map for each dataset
    # group_by(TaxonKey,
    #          INDEX
    # ) %>%
    # summarise(Model_Index = mean(Value,na.rm=T)
    #           ) %>%
    # filter(Model_Index > 0) %>%
    #____________ ESTIMATING FUNDAMENTAL NICHE (TRESHOLD 2)_________ #
    # left_join(SppDist,
    #           by = c("TaxonKey","INDEX")) %>% 
    # filter(Model == "SAU_C", # Only keeping cells where SAU catch exists
    #        Value > 0) %>%
    # mutate(Model_Index = Model_Index*100) %>% 
    # select(-Model, -Value, -Latitude,-Longitude) %>% 
    left_join(EEZ_CellID,
              by = "INDEX") %>% 
    left_join(EEZIDs_List,
              by = "EEZID")

  # MODEL INDEX (TRESHOLDS 1 & 2) #
  Model_Index_D <- Trans_Spp %>% 
    group_by(Name,
             TaxonKey,
             # Model_Index, # Un-comment after producing models x datasets
             Model # Remove after producing models x datasets
    ) %>% 
    summarise(n_cells_spp = n()) %>% 
    select(-n_cells_spp)

@@

  # Step 2. Determines the amount of grids present in each country
  Spp_Grid <- Trans_Spp %>% 
    group_by(TaxonKey,
             # Model_Index, # Un-comment after producing models x datasets
             Model, # Remove after producing models x datasets
             EEZID) %>% 
    summarise(n_spp_eez = length(unique(INDEX))) %>% 
    left_join(Neighbors_EEZ,
              by = "EEZID") %>% 
    filter(Country_Territory %in% Trans_Spp$Name, #Filter out unwanted neighbors (those who don't have grids within but get included because they are neighbors)
           Neighbor_Territory %in% Trans_Spp$Name)

@@

  # Split dataframes to merge latter
  Country_Territory_T <- Spp_Grid %>% 
    ungroup() %>% 
    select(
      # Model_Index, # Un-comment after producing models x datasets
      Model, # Remove after producing models x datasets
      TaxonKey,Name=Country_Territory,n_spp_eez
    )

  Neighbor_Territory_T <- Spp_Grid %>% 
    ungroup() %>% 
    select(
      # Model_Index,
      Model, # Remove after producing models x datasets
      TaxonKey,n_spp_eez,Name=Neighbor_Territory, Country_Territory
    )

  # Merge dataframes to get totals per neighbords
  Area_Index_D <- full_join(Country_Territory_T,
                           Neighbor_Territory_T, by = c(#"Model_Index",
                             "Name","TaxonKey","Model")) %>% # Remove Model abd undomment Model_Index after producing Models x datasets
    rowwise() %>%
    mutate(Spp_Total = sum(n_spp_eez.x,n_spp_eez.y,na.rm=T)) %>% # Total gridcelles per neighbors
    distinct() %>% # Removes false duplicates from `full_join()`
    rename(Neighbor_Territory = Name,
           n_spp_Country = n_spp_eez.x,
           n_spp_Neighbor = n_spp_eez.y) %>% 
    mutate(Area_Index = n_spp_Country/Spp_Total) %>%  #Estimates the proportion of grids per country
    # select(1:3,6,8) # Commented out for all models analysis
    select(1:4,6,8)

  #____________ FINAL INDEX TABLE_________ #
  Indexes <- Model_Index_D %>% 
  rename(Country_Territory = Name) %>% 
  full_join(Area_Index_D,
            by = c("TaxonKey","Country_Territory",
                   #"Model_Index"
                   "Model") # Remove Model abd undomment Model_Index after producing Models x datasets
  ) %>% 
    filter(!is.na(Area_Index)#,
           # !is.na(Model_Index) # Uncomment after producing Models x datasets
           )%>%  # Remove cases where the country does not pass the area_index and viceversa
    select(Model,TaxonKey,Country_Territory,Neighbor_Territory,everything())

@@

@@

@@

# Creates dummy dataset for Non transboundary species
write.csv(tibble(Non_trans = "NA"), paste(Results_Path,"Non_Transboundary_Data.csv",sep=""), row.names = F)

@@

@@

@@

@@

>>>>

#### Library ####
packages <- c(
  "readxl", # Read dataframe
  "data.table", # Read dataframe (Fast!)
  "dplyr", # Data manipulation
  "tidyr", # Data manipulation
  "ggplot2", #Nice grpahs and spatial analysis
  "wesanderson",
  "circlize", # For circular plot
  # "cowplot",
  # "rgdal",
  # "RColorBrewer",
  # "knitr",
  # "kableExtra",
  # "ggrepel",
  # "gridExtra",
  # "ggmap",
  # "rgeos",
  # "stringr",
  # "stringer",
  "spdep", # for poly2nb
  "sf", #Spatial analysis 
  "sp", #Spatial analysis 
  "purrr",#Spatial analysis
  "rgdal", #Spatial analysis
  "tools", #Spatial analysis 
  # "png", # For reading plots in chunk codes
  # "grid" # For reading plots in chunk codes
  "parallel" # for parallelization
)

@@

# The function
EstTransIndex_All <- function(Spp,Model,Neighbors,Coord,Save="Y"){

@@

  #____________ ESTIMATING MODEL INDEX (TRESHOLD 1)_________ #
  Trans_Spp <- SppDist %>%
    filter(INDEX %in% Neighbors$INDEX,# Filter data only located within EEZs
           Model != "SAU_C") %>% # Only using observational and modelled data
    mutate(Value = ifelse(Value > 0, 1,0)) %>%  
    filter(Value > 0) %>%
    group_by(TaxonKey,
             INDEX
    ) %>%
    summarise(Model_Index = mean(Value,na.rm=T)
              ) %>%
    filter(Model_Index > 0) %>%
    # ____________ ESTIMATING FUNDAMENTAL NICHE (TRESHOLD 2)_________ #
    left_join(SppDist,
              by = c("TaxonKey","INDEX")) %>%
    filter(Model == "SAU_C", # Only keeping cells where SAU catch exists
           Value > 0) %>%
    mutate(Model_Index = Model_Index*100) %>%
    select(-Model, -Value, -Latitude,-Longitude) %>%
    left_join(EEZ_CellID,
              by = "INDEX") %>% 
    left_join(EEZIDs_List,
              by = "EEZID")

  # MODEL INDEX (TRESHOLDS 1 & 2) #
  Model_Index_D <- Trans_Spp %>% 
    group_by(Name,
             TaxonKey,
             Model
             ) %>% 
    summarise(n_cells_spp = n()) %>% 
    select(-n_cells_spp)

@@

  # Step 2. Determines the amount of grids present in each country
  Spp_Grid <- Trans_Spp %>% 
    group_by(TaxonKey,
             Model_Index, # Un-comment after producing models x datasets
             EEZID) %>% 
    summarise(n_spp_eez = length(unique(INDEX))) %>% 
    left_join(Neighbors_EEZ,
              by = "EEZID") %>% 
    filter(Country_Territory %in% Trans_Spp$Name, #Filter out unwanted neighbors (those who don't have grids within but get included because they are neighbors)
           Neighbor_Territory %in% Trans_Spp$Name)

@@

  # Split dataframes to merge latter
  Country_Territory_T <- Spp_Grid %>% 
    ungroup() %>% 
    select(
      Model_Index, # Un-comment after producing models x datasets
      TaxonKey,
      Name=Country_Territory,
      n_spp_eez
    )

  Neighbor_Territory_T <- Spp_Grid %>% 
    ungroup() %>% 
    select(
      Model_Index,
      TaxonKey,n_spp_eez,
      Name=Neighbor_Territory, 
      Country_Territory
    )

  # Merge dataframes to get totals per neighbords
  Area_Index_D <- full_join(Country_Territory_T,
                           Neighbor_Territory_T, 
                           by = c("Model_Index","Name","TaxonKey")
                           ) %>%
    rowwise() %>%
    mutate(Spp_Total = sum(n_spp_eez.x,n_spp_eez.y,na.rm=T)) %>% # Total gridcelles per neighbors
    distinct() %>% # Removes false duplicates from `full_join()`
    rename(Neighbor_Territory = Name,
           n_spp_Country = n_spp_eez.x,
           n_spp_Neighbor = n_spp_eez.y) %>% 
    mutate(Area_Index = n_spp_Country/Spp_Total) %>%  #Estimates the proportion of grids per country
    select(1:3,6,8)

  #____________ FINAL INDEX TABLE_________ #
  Indexes <- Model_Index_D %>% 
  rename(Country_Territory = Name) %>% 
  full_join(Area_Index_D,
            by = c("TaxonKey","Country_Territory","Model_Index")
            ) %>% 
    filter(!is.na(Area_Index),
           !is.na(Model_Index) # Uncomment after producing Models x datasets
           )%>%  # Remove cases where the country does not pass the area_index and viceversa
    select(TaxonKey,Country_Territory,Neighbor_Territory,everything())

@@

    # Get current Spp that is not transboundary 
    Current_Spp <- tibble(TaxonKey = Spp)

@@

}
```

@@

# Creates dummy dataset for Non transboundary species
write.csv(tibble(TaxonKey = "NA"), paste(Results_Path,"Non_Transboundary_Data.csv",sep=""), row.names = F)

@@

# Data on time for the Beast with 30 cores
# user   system  elapsed 
 #8117.72  1991.91 10296.00

@@

# For Carmelia
Clean_Results_Trans <- read.csv(paste(Data_Path,"Clean_Results.csv",sep=""))

@@

```{r Circle_Diagram, eval =F, echo = F}

Test_Data <- Clean_Results_Trans %>% 
  rename(FishingRegion=Country_Territory) %>% 
  left_join(Clean_sau_eez_fes,
            by = "FishingRegion") %>% 
  select(TaxonKey,
         Country_Territory= FishingRegion,
         FishingRegion=Neighbor_Territory,
         Model_Index,
         Area_Index,
         CT_fishing_entity= fishing_entity) %>% 
  left_join(Clean_sau_eez_fes,
            by = "FishingRegion") %>% 
  select(1,2, 
    Neighbor_Territory = FishingRegion,
    Model_Index:CT_fishing_entity,
    NT_fishing_entity = fishing_entity,
    everything()
  ) %>% 
  mutate(
    # CT_fishing_entity = ifelse(is.na(CT_fishing_entity),paste(Country_Territory),paste(CT_fishing_entity)),
    # NT_fishing_entity = ifelse(is.na(NT_fishing_entity),paste(Neighbor_Territory),paste(NT_fishing_entity)),
    Same_Nation = ifelse(CT_fishing_entity==NT_fishing_entity,"Yes","No")
  ) %>% 
  filter(Model_Index == 100,
         Area_Index >= 0.25,
         Area_Index <= 0.75,
         Same_Nation == "No"
         ) %>% 
  group_by(from=CT_fishing_entity,
           to = NT_fishing_entity,
           Model_Index
           ) %>% 
  summarise(value = length(unique(TaxonKey))) %>% 
  # filter(from %in% c("Chile","Brazil","Argentina","Peru","Equator")) %>%
  select(from,to,value)

####________________###
# Circulize package ####
####________________###

col_mat = rand_color(length(Test_Data), transparency = 0.5)
col_mat[Test_Data < 10] = "#00000000"

chordDiagram(Test_Data, annotationTrack = "grid")

circos.track(track.index = 1, panel.fun = function(x, y) {
    circos.text(CELL_META$xcenter, CELL_META$ylim[1], CELL_META$sector.index, 
        facing = "clockwise", niceFacing = TRUE, adj = c(0, 0.5))
}, bg.border = NA) # here set bg.border to NA is important

@@

# Extra Analysis

## Extra Analysis; Functions

```{r Trans_Spp_Function_All, eval = F ,echo = T,warning = F,message = F}

# Function to determine whether or not a species is transboundary for each model

  #____________ ESTIMATING MODEL INDEX (TRESHOLD 1)_________ #
  Trans_Spp <- SppDist %>%
    filter(INDEX %in% Neighbors$INDEX,# Filter data only located within EEZs
           Model != "SAU_C") %>% # Only using observational and modelled data
    mutate(Value = ifelse(Value > 0, 1,0)) %>%
    left_join(EEZ_CellID,
              by = "INDEX") %>% 
    left_join(EEZIDs_List,
              by = "EEZID")

  # MODEL INDEX (TRESHOLDS 1 & 2) #
  Model_Index_D <- Trans_Spp %>% 
    group_by(Name,
             TaxonKey,
             Model
    ) %>% 
    summarise(n_cells_spp = n()) %>% 
    select(-n_cells_spp)

  # Step 2. Determines the amount of grids present in each country
  Spp_Grid <- Trans_Spp %>% 
    group_by(TaxonKey,
             Model, 
             EEZID) %>% 
    summarise(n_spp_eez = length(unique(INDEX))) %>% 
    left_join(Neighbors_EEZ,
              by = "EEZID") %>% 
    filter(Country_Territory %in% Trans_Spp$Name, #Filter out unwanted neighbors (those who don't have grids within but get included because they are neighbors)
           Neighbor_Territory %in% Trans_Spp$Name)

  # Split dataframes to merge latter
  Country_Territory_T <- Spp_Grid %>% 
    ungroup() %>% 
    select(
      Model_Index, # Un-comment after producing models x datasets
      TaxonKey,Name=Country_Territory,n_spp_eez
    )

  Neighbor_Territory_T <- Spp_Grid %>% 
    ungroup() %>% 
    select(
      Model_Index,
      TaxonKey,n_spp_eez,Name=Neighbor_Territory, Country_Territory
    )

  # Merge dataframes to get totals per neighbords
  Area_Index_D <- full_join(Country_Territory_T,
                           Neighbor_Territory_T, by = c("Name","TaxonKey","Model")) %>%
    rowwise() %>%
    mutate(Spp_Total = sum(n_spp_eez.x,n_spp_eez.y,na.rm=T)) %>% # Total gridcelles per neighbors
    distinct() %>% # Removes false duplicates from `full_join()`
    rename(Neighbor_Territory = Name,
           n_spp_Country = n_spp_eez.x,
           n_spp_Neighbor = n_spp_eez.y) %>% 
    mutate(Area_Index = n_spp_Country/Spp_Total) %>%  #Estimates the proportion of grids per country
    select(1:4,6,8)

  #____________ FINAL INDEX TABLE_________ #
  Indexes <- Model_Index_D %>% 
  rename(Country_Territory = Name) %>% 
  full_join(Area_Index_D,
            by = c("TaxonKey","Country_Territory","Model")
  ) %>% 
    filter(!is.na(Area_Index))%>%  # Remove cases where the country does not pass the area_index and viceversa
    select(Model,TaxonKey,Country_Territory,Neighbor_Territory,everything())

    File_Name <- paste(Spp,"_Transboundary.csv",sep = "")
    Save_Path <- paste(Results_Path,"All_Models/",File_Name,sep="")

# Reads dataset of Non transboundary species
    Non_Transboundary_Data <- fread(paste(Results_Path,"All_Models/","Non_Transboundary_Data.csv",sep=""))

    # Set a name for file and saves data
    New_Non_Name <- paste(Results_Path,"All_Models/","Non_Transboundary_Data.csv",sep="")
    write.csv(New_Non, New_Non_Name, row.names = F)

## Extra Analysis; Results

```{Tran_country_Map_All, eval =F, echo =F}

pal <- wes_palette("Zissou1", 100, type = "continuous")

Mod <- unique(TenTwenyfive$Model)

# Loop through all variables
for(v in 1:length(Mod)){

  Model_List <- Mod[v]

  plot <- ggplot(data = subset(World_EEZs_simple,Model %in% Model_List)) +
    geom_sf(aes(fill = n_trans)) +
    scale_fill_gradientn(colours = pal,
                         na.value = "white") +
    ggtheme_map() +
    ggtitle(paste(Model_List))

  # Name plot
  Plot_Name <- paste(Model_List,"plot.png",sep="_")

  # Save plot
  ggsave(
    plot = plot,
    width = 14,
    height = 10,
    units = "in",
    filename = Plot_Name,
    path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/All_Models/"
  )
